ms_willow_network_supplement

### 2015-04-06 ms_willow_network_supplement.Rmd
lots of additions.

## load required libraries
#library(vegan) # for adonis analysis
#library(knitr) # for making tables
library(ggplot2) # for plotting
theme_set(theme_classic()) # customize ggplot for prettier default graphs
library(gridExtra) # for grid.arrange
library(mvabund) # multivariate analysis
library(HH) # for variance inflation factor analysis (vif) in multiple regression

@@

Boxplots of gall abundance among the different genotypes.
```{r gall abund across genotypes, echo = FALSE}
vLG.abund.plot <- ggplot(data = full.df, aes(x = Genotype, y = vLG_abund)) + 
  geom_boxplot() + ylab("Iteomyia salicisverruca density (#/branch)")
rG.abund.plot <- ggplot(data = full.df, aes(x = Genotype, y = rG_abund)) + 
  geom_boxplot() + ylab("Rabdophaga salicisbrassicoides density (#/branch)")
aSG.abund.plot <- ggplot(data = full.df, aes(x = Genotype, y = aSG_abund)) + 
  geom_boxplot() + ylab("Cecidomyid sp. A density (#/branch)")
SG.abund.plot <- ggplot(data = full.df, aes(x = Genotype, y = SG_abund)) + 
  geom_boxplot() + ylab("Rabdophaga salicisbattatus density (#/branch)")

grid.arrange(vLG.abund.plot, rG.abund.plot, aSG.abund.plot, SG.abund.plot)
```

@@

N <- 50
link.div.list <- list()
for(i in 1:N){
  link.div.list[[i]] <- round(predict.allcombos(manyglm.full, factor.index = 2), 1)
} # takes a couple minutes with 50 reps

link.div.df <- ldply(link.div.list) %>% tbl_df()
link.div.df$diversity <- diversity(select(link.div.df, aSG_Tory:vLG_Tory))
link.div.df$repID <- 1:dim(link.div.df)[1]

@@

link.melt <- melt(select(link.div.df, -diversity), id.vars = c("repID", "Number.of.Genotypes"))

@@

library(bipartite)
web.list.measures <- c()
genotype.number <- c()
for(i in 1:dim(web.list)){
  genotype.number[i] <- names(web.list[[i]][1])
  tmp.web <- web.list[[i]][[1]]
  rownames(tmp.web) <- tmp.web$gall
  tmp.web <- as.matrix.data.frame(tmp.web[ ,-1])
  web.list.measures[i] <- networklevel(tmp.web, index = "linkage density", weighted = TRUE)
}
web.measures.df <- cbind.data.frame(Number.of.Genotypes = as.numeric(genotype.number),
                                    Weighted.Linkage.Density = web.list.measures)

@@

@@

library(mgcv)
web.sum.lm <- lm(log(median.link.density) ~ log(Number.of.Genotypes), data = web.measures.summary)
summary(web.sum.lm) # Need to understand interpretation here.
visreg(web.sum.lm) # not quite there
```

@@

Here, we evaluate the assumptions of mvabund and see which error distribution is appropriate. Specifically, we first look at a plot of the mean-variance relationship of our response variables. It is easy to see that the negative binomial model (black line) provides the best fit to this data, suggesting that we should specify this as the error distribution in our model
```{r mv abund interactions explore}
full.mvabund <- mvabund(full.df[ ,interaxns_noPont]) # create mvabund object for easy analysis
meanvar.plot(full.mvabund ~ full.df$Genotype) # easy to see that the data do not have a poisson distribution, therefore, a negative binomial may be a good fit.
poisson_curve(from = 0.1, to = 3.0, color = "blue")
quasipoisson_curve(from = 0.1, to = 3.0, quasi.scalar = 2, color = "red")
neg.binomial_curve(from = 0.1, to = 3.0, theta.negbin = 0.7, color = "black") # negative binomial appears to provide the best fit to this relationship
```

@@

From the table, it is clear to say that genotype has a strong effect on the composition of links in the network. Moreover, differences in community composition are driven primarily by 3 interactions: vLG_Platy, vLG_Tory, and vLG_Mesopol.
```{r}
anova.full <- anova.manyglm(manyglm.full, p.uni = "unadjusted") # Takes about 1 min and 30 sec to run.
anova.full # vLG_Platy, vLG_Tory, and vLG_Mesopol are driving the community response. rG_Tory is marginally significant and vLG_Eulo is close to marginal as well.
```

@@

First we created a dataset that contained complete observations of the network and predictor variables
```{r mv abund interaction predictors}
full.predictors <- full.df %>%
  select(aSG_Tory:rG_Platy, rG_Tory, SG_Platy, vLG_Eulo:vLG_Tory, # interactions
         aSG_abund:vLG_abund, # gall counts. Exclusing SG_abund because it didn't vary among genotypes
         vLG.height.mean) %>% # Iteomyia gall size
# we transformed some of the variables so we could examine their vif 
  mutate(log.vLG_abund = log(vLG_abund),
         log.1.vLG_abund = log(vLG_abund + 1),
         log.1.rG_abund = log(rG_abund + 1),
         log.1.aSG_abund = log(aSG_abund + 1),
         log.vLG.height.mean = log(vLG.height.mean)) %>%
  na.omit() # removes all instances that don't have vLG.height.mean
dim(full.predictors)[1] # 81 data points
```

@@

We log transformed all predictor variables because it provided a much better fit to the data as determined by AIC. We then used AIC to compare our most complex model to our least complex. Instead of exploring all possible combinations, we started with the most complex model and used AIC to drop predictor variables with the lowest AIC values (i.e. least impact on removal). Using AIC, we identified 3 equivalenet models (difference in AIC < 2.1 amongst models). 
```{r AIC model assessment}
net.trait <- mvabund(full.predictors[ ,interaxns_noPont])
net.trait.sub <- mvabund(full.predictors[ ,c("vLG_Platy","vLG_Mesopol","vLG_Tory","rG_Tory")])
# even though manyglm doesn't appear to test interaction terms appropriately (sequential vs. dropping different terms), there is not interactive effect of vLG height and vLG abundance in univariate negative binomial models for any vLG_parasitoid interaction, so I believe this final model is appropriate for the data.
net.mvabund.1.full <- manyglm(net.trait ~ log.vLG_abund*vLG.height.mean + 
                         log.1.rG_abund + log.1.aSG_abund,
                       data = full.predictors,
                       family = "negative.binomial")
MASS::stepAIC(net.mvabund.1.full, direction = "both")

@@

After deciding on the model with all main effects and no interactions, we examined the residuals and everything looked pretty good.
```{r}
plot(net.mvabund.2, which = 1:3) # residuals look pretty good.
```

@@

sig.coef.df.2 <- mutate(melt(coef(net.mvabund.2)),
               predictor_response = paste(X1, X2, sep = "_")) %>%
 # select(predictor = X1, response = X2, predictor_response, value) %>%
  subset(predictor_response %in% c("log.1.aSG_abund_aSG_Tory", 
                                 "log.1.rG_abund_rG_Eulo",
                                 "log.1.rG_abund_rG_Platy",
                                 "log.1.rG_abund_rG_Lestodip", # marginal
                                 "log.vLG_abund_SG_Platy", # marginal
                                 "log.vLG_abund_vLG_Mymarid",
                                 "log.vLG.height.mean_vLG_Eulo", # marginal
                                 "log.vLG.height.mean_rG_Tory", "log.1.rG_abund_rG_Tory",
                                 "log.vLG_abund_vLG_Mesopol", "log.vLG.height.mean_vLG_Mesopol", 
                                 "log.vLG.height.mean_vLG_Platy", "log.vLG_abund_vLG_Platy",
                                 "log.vLG.height.mean_vLG_Tory", "log.vLG_abund_vLG_Tory")) %>% # vLG.height.mean is marginal for vLG_Tory
  select(predictor = X1, response = X2, coefficient = value)
arrange(sig.coef.df.2, predictor, response)
```

>>>>

## load required libraries
#library(vegan) # for adonis analysis
#library(knitr) # for making tables
library(ggplot2) # for plotting
theme_set(theme_bw()) # customize ggplot for prettier default graphs
library(gridExtra) # for grid.arrange
library(mvabund) # multivariate analysis
library(HH) # for variance inflation factor analysis (vif) in multiple regression

@@

Boxplots of gall abundance among the different genotypes.
```{r gall abund across genotypes, echo = FALSE}
gall.plot.df <- as.data.frame(full.df) %>% # melt doesn't like 'tbl' class
  select(Genotype, 
         Iteomyia_salicisverruca = vLG_abund,
         Cecidomyiid_sp.A = aSG_abund,
         Rabdophaga_salicisbrassicoides = rG_abund, 
         Rabdophaga_salicisbattatus = SG_abund) %>%
  melt()

ggplot(gall.plot.df, aes(x = Genotype, y = value, color = variable)) + 
  geom_boxplot() + facet_wrap( ~ variable, nrow = 2) + theme_bw() + ylab("Gall density (#/branch)")
```

@@

N <- 1000
link.div.list <- list()
for(i in 1:N){
  link.div.list[[i]] <- round(predict.allcombos(manyglm.full, factor.index = 2), 1)
} # takes a couple minutes with 50 reps
#library(vegan)
link.div.df <- ldply(link.div.list) %>% tbl_df()
link.div.df$diversity <- diversity(select(link.div.df, aSG_Tory:vLG_Tory))
link.div.df$repID <- 1:dim(link.div.df)[1]

# get predicted weighted linkage density for each genotype
predict.single.geno <- as.data.frame(round(predict.manyglm(manyglm.full, data.frame(Genotype = levels(full.df$Genotype)), type = "response"),1))
predict.single.geno$Number.of.Genotypes <- rep(1, 26)
predict.single.geno$diversity <- diversity(select(predict.single.geno, -Number.of.Genotypes))
predict.single.geno$repID <- 25001:(25001+25)

link.div.df <- rbind.data.frame(link.div.df, predict.single.geno)

@@

link.melt <- as.data.frame(link.div.df) %>%
  select(-diversity) %>%
  melt(id.vars = c("repID", "Number.of.Genotypes"))

@@

single.web.list <- cast(filter(link.melt.df, Number.of.Genotypes == 1), gall ~ parasitoid | repID, mean)

#library(bipartite)
web.list.measures <- c()
genotype.number <- c()
for(i in 1:dim(web.list)){
  genotype.number[i] <- names(web.list[[i]][1])
  tmp.web <- web.list[[i]][[1]]
  rownames(tmp.web) <- tmp.web$gall
  tmp.web <- as.matrix.data.frame(tmp.web[ ,-1])
  web.list.measures[i] <- networklevel(tmp.web, index = "linkage density", weighted = TRUE)
}

single.web.list.measures <- c()
single.genotype.number <- c()
for(i in 1:dim(web.list)){
  genotype.number[i] <- names(single.web.list[[i]][1])
  tmp.web <- single.web.list[[i]][[1]]
  rownames(tmp.web) <- tmp.web$gall
  tmp.web <- as.matrix.data.frame(tmp.web[ ,-1])
  web.list.measures[i] <- networklevel(tmp.web, index = "linkage density", weighted = TRUE)
}

web.measures.df <- cbind.data.frame(Number.of.Genotypes = as.numeric(genotype.number),
                                    Weighted.Linkage.Density = web.list.measures)

@@

write.csv(web.measures.df, "web.measures.df.csv")

ggplot(web.measures.df, 
       aes(x = Number.of.Genotypes, y = Weighted.Linkage.Density)) + 
  geom_jitter(shape = 1, color = "grey", position = position_jitter(width = 0.15, height = NULL)) + 
  stat_summary(fun.y = mean, geom = "point", color = "steelblue", size = 8) + 
  xlab("Genetic variation (# of genotypes)") + ylab("Weighted linkage density") +
  scale_x_continuous(limits = c(0,26), breaks = 1:26) +
  theme_bw() + 
  theme(axis.text = element_text(size = 14),
        axis.title.x = element_text(size = 16, vjust = 0.1),
        axis.title.y = element_text(size = 16, vjust = 1),
        panel.grid = element_blank())

@@

#library(mgcv)
#library(visreg)
web.sum.lm <- lm(log(median.link.density) ~ log(Number.of.Genotypes), data = web.measures.summary)
summary(web.sum.lm) # Need to understand interpretation here.
visreg(web.sum.lm) # not quite there
```

```{r complementarity}
net.pred.geno <- as.data.frame(round(predict.manyglm(manyglm.full, 
                                       newdata = data.frame(Genotype = levels(full.df$Genotype)), 
                                       type = "response"), 1)) %>% # round to avoid pseudoaccuracy 
  mutate(Genotype = levels(full.df$Genotype)) %>%
  melt(id.vars = "Genotype")

net.split <- colsplit(net.pred.geno$variable, pattern = "_", names = c("gall","parasitoid"))
net.pred.geno.df <- cbind(net.pred.geno, net.split)

net.pred.full.df <- net.pred.geno.df %>%
  group_by(variable, gall, parasitoid) %>%
  summarise(value = mean(value))

net.list <- cast(net.pred.geno.df, gall ~ parasitoid | Genotype, mean)
net.list.noU <- net.list[-21]

net.full <- cast(net.pred.full.df, gall ~ parasitoid, mean)
rownames(net.full) <- net.full$gall
net.full <- as.matrix.data.frame(net.full[ ,-1]) # remove gall variable
net.full.measure <- networklevel(net.full, index = c("links per species", "linkage density", "Shannon diversity"), weighted = TRUE) # note that the weighted linkage density here is higher than from my simulation with the 26 genotypes...

library(bipartite)
nets <- list()
net.list.measures <- c()
genotypes <- c()
for(i in 1:dim(net.list.noU)){
  genotypes[i] <- names(net.list.noU)[i]
  tmp.web <- net.list.noU[[i]]
  rownames(tmp.web) <- tmp.web$gall
  nets[[i]] <- as.matrix.data.frame(tmp.web[ ,-1])
  net.list.measures[i] <- networklevel(nets[[i]], index = "linkage density", weighted = TRUE)
}
mean(net.list.measures)
genotypes
net.list.measures.df <- cbind.data.frame(genotypes, net.list.measures)
networklevel(nets[[25]], index = c("links per species", "linkage density", "Shannon diversity"), weighted = TRUE)

qplot(net.list.measures.df, x = factor(1), y = net.list.measures, fill = genotypes, , color = "black", geom = "bar", stat = "identity")
sum(net.list.measures.df$net.list.measures)

ph <- matrix(c(1,1,1), nrow = 1)
networklevel(ph, index = c("links per species", "linkage density", "Shannon diversity", "vulnerability", "generality"), weighted = TRUE)
mean(c(3,1,3,1))
```

@@

Here, we evaluate the assumptions of mvabund and see which error distribution is appropriate. Specifically, we first look at a plot of the mean-variance relationship of our response variables. It is easy to see that the negative binomial model (black line) provides the best fit to this data, suggesting that we should specify this as the error distribution in our model
```{r mv abund interactions explore}
full.mvabund <- mvabund(full.df[ ,interaxns_noPont]) # create mvabund object for easy analysis
full.meanvar <- meanvar.plot(full.mvabund ~ full.df$Genotype, table = TRUE) # easy to see that the data do not have a poisson distribution, therefore, a negative binomial may be a good fit.
poisson_curve(from = 0.1, to = 3.0, color = "blue")
quasipoisson_curve(from = 0.1, to = 3.0, quasi.scalar = 2, color = "red")
neg.binomial_curve(from = 0.1, to = 3.0, theta.negbin = 0.7, color = "black") # negative binomial appears to provide the best fit to this relationship

no.relationships <- which(names(colSums(full.mvabund)) %in% c("rG_Lestodip", "rG_Mesopol", "SG_Platy", "vLG_Eulo"))
sum(colSums(full.mvabund)[no.relationships])/sum(colSums(full.mvabund)) # less than 13% of the links in the network had relationships to gall abundance and size (see results below)
```

Analysis of dissimilarity in interaction composition
```{r}
links <- full.df[ ,interaxns_noPont] 
link_abund <- rowSums(links)

links.dist <- cbind.data.frame(Genotype = full.df$Genotype, links) %>%
  filter(link_abund > 0, Genotype %in% c("*","A","B","D","E","F","I","K","L","Q","S","T","V","W","X","Y","Z"))

links.geno.dist <- meandist(vegdist(links.dist[ ,-1], "bray"), links.dist$Genotype)
summary(links.geno.dist) # on average, gall communities were 57% dissimilar from each other
plot(links.geno.dist, cluster = "ward")
```

@@

From the table, it is clear to say that genotype has a strong effect on the composition of links in the network. Moreover, differences in community composition are driven primarily by 3 interactions: vLG_Platy, vLG_Tory, and vLG_Mesopol.
```{r}
anova.full <- anova.manyglm(manyglm.full, p.uni = "unadjusted") # Takes about 1 min and 30 sec to run.
anova.full # vLG_Platy, vLG_Tory, and vLG_Mesopol are driving the community response. rG_Tory is marginally significant and vLG_Eulo is close to marginal as well. aSG_Tory is significant as well.
```

```{r}
full.mean <- cbind.data.frame(Genotype = full.df$Genotype, full.mvabund) %>%
  group_by(Genotype) %>%
  summarise_each(funs(mean.narm = mean(., na.rm = TRUE)))

# calculate average dissimilarity in link community composition among willow genotypes using average link abundance data.
require(vegan)
full.mean.df.noU <- full.mean %>% filter(Genotype != "U") # genotype U never had any interactions
full.mean.bray <- vegdist(select(full.mean.df.noU, -Genotype), method = "bray")
mean(full.mean.bray) # on average, link composition was 77% dissimilar from each other.
sd(full.mean.bray)
range(full.mean.bray)

plot(hclust(full.mean.bray, method = "average"), labels = full.mean.df.noU$Genotype)
#NMDS <- metaMDS(comm = select(full.mean.df.noU, -Genotype), distance = "bray")
#plot(NMDS, type = "t")

require(tidyr)
beta_partition_lists <- as.data.frame(full.mean.df.noU) %>%
  gather(key = Genotype, value = link_abund, aSG_Tory:vLG_Tory) %>% # why don't variable and value columns change?
  #mutate(variable = as.character(variable)) %>%
  separate(variable, into = c("Gall","Parasitoid"), sep = "_") %>%
  filter(value > 0) %>%
  cast(Gall ~ Parasitoid | Genotype, sum) # note that sum function doesn't do anything. I'm just reshaping the dataframe into multiple lists.
beta_partition_lists <- beta_partition_lists[-21]

for(i in 1:length(beta_partition_lists)) {
  rownames(beta_partition_lists[[i]]) <- as.character(beta_partition_lists[[i]]$Gall) # change row names to gall specie names
  beta_partition_lists[[i]] <- as.data.frame(select(beta_partition_lists[[i]], -Gall)) # remove gall.sp as a column of data. Turning this into a matrix is important for easier analysis with betalink package
  beta_partition_lists[[i]] <- as.matrix(beta_partition_lists[[i]])  # need to be converted into matrices for "as.table" function to work for quantitative data.
}

### Beta-diversity of interaction network analysis
source('~/Documents/betalink/R/betalink.R')
source('~/Documents/betalink/R/vec2data.frame.R')
source('~/Documents/betalink/R/measures.r')
source('~/Documents/betalink/R/betalink.b.r')
source('~/Documents/betalink/R/betalink.dist.r')
source('~/Documents/betalink/R/betalink.q.R')

# Betalink Quantitative
betalink_quantitative <- betalink.dist(beta_partition_lists, bf = "bray", triangular = T) #
betalink_qualitative <- betalink.dist(beta_partition_lists, bf = B01, triangular = T)

mean(betalink_quantitative$WN) # 77% dissimilarity with bray
mean(betalink_qualitative$WN) # 63% dissimilarity with whittaker

mean(betalink_quantitative$OS) # 33% with bray
mean(betalink_qualitative$OS) # 6% with whittaker

mean(betalink_quantitative$ST) # 44% with bray
mean(betalink_qualitative$ST) # 57% with whittaker

mean(betalink_quantitative$contrib) # species turnover contributes to 53% of the dissimilarity in interaction networks, according to bray-curtis
mean(betalink_qualitative$contrib) # species turnover contributes to 86% of the dissimilarity in interaction networks, according to whittaker index on qualitative data.
```

@@

First we created a dataset that contained complete observations of the network and predictor variables
```{r mv abund interaction predictors}
full.predictors <- full.df %>%
  select(aSG_Tory:rG_Platy, rG_Tory, SG_Platy, vLG_Eulo:vLG_Tory, # interactions
         aSG_abund:vLG_abund, # gall counts. Exclusing SG_abund because it didn't vary among genotypes
         Genotype, # keeping for later analysis
         vLG.height.mean) %>% # Iteomyia gall size
# we transformed some of the variables so we could examine their vif 
  mutate(log.vLG_abund = log(vLG_abund),
         log.1.vLG_abund = log(vLG_abund + 1),
         log.1.rG_abund = log(rG_abund + 1),
         log.1.aSG_abund = log(aSG_abund + 1),
         log.vLG.height.mean = log(vLG.height.mean)) %>%
  na.omit() # removes all instances that don't have vLG.height.mean
dim(full.predictors)[1] # 81 data points
```

@@

We log transformed all predictor variables because it provided a much better fit to the data as determined by AIC. We then used AIC to compare our most complex model to our least complex. Instead of exploring all possible combinations, we started with the most complex model and used AIC to drop predictor variables with the lowest AIC values (i.e. least impact on removal). Using AIC, we identified 3 equivalenet models (difference in AIC < 2.1 amongst models). 
```{r AIC model assessment}
net.trait <- mvabund(full.predictors[ ,interaxns_noPont])

interactions <- full.predictors[ ,interaxns_noPont]
interactions[interactions > 0] <- 1

net.trait.sub <- mvabund(interactions)
# even though manyglm doesn't appear to test interaction terms appropriately (sequential vs. dropping different terms), there is not interactive effect of vLG height and vLG abundance in univariate negative binomial models for any vLG_parasitoid interaction, so I believe this final model is appropriate for the data.
net.mvabund.pres <- manyglm(net.trait.sub ~ log.vLG_abund + vLG.height.mean + log.1.rG_abund + log.1.aSG_abund, data = full.predictors, family = "binomial")
plot(net.mvabund.pres, which = 1:3)
anova.qual <- anova(net.mvabund.pres, p.uni = "unadjusted")
anova.qual

summary(glm(cbind(rG_Tory, rG_Platy + rG_Eulo + rG_Lestodip + rG_Mesopol) ~ vLG.height.mean, data = full.predictors, family = "binomial"))
visreg(glm(cbind(vLG_Tory, vLG_Platy + vLG_Eulo + vLG_Mymarid + vLG_Mesopol) ~ vLG.height.mean + vLG_abund, data = full.predictors, family = "binomial"), scale = "response")

net.mvabund.1.full <- manyglm(net.trait ~ log.vLG_abund*vLG.height.mean + 
                         log.1.rG_abund + log.1.aSG_abund,
                       data = full.predictors,
                       family = "negative.binomial")
MASS::stepAIC(net.mvabund.1.full, direction = "both")

@@

After deciding on the model with all main effects and no interactions, we examined the residuals and everything looked pretty good.
```{r}
plot(net.mvabund.2, which = 1:3) # residuals look pretty good.

plot(MASS::glm.nb(vLG_Platy ~ vLG_abund + vLG.height.mean, full.predictors))
```

@@

anova.net.null <- anova.manyglm(net.mvabund.2, net.mvabund.6.null) # takes about 30 sec to run
anova.net.null

sig.coef.df.2 <- mutate(melt(coef(net.mvabund.2)),
               predictor_response = paste(X1, X2, sep = "_")) %>%
 # select(predictor = X1, response = X2, predictor_response, value) %>%
  subset(predictor_response %in% c("log.1.aSG_abund_aSG_Tory", 
                                 "log.1.rG_abund_rG_Eulo",
                                 "log.1.rG_abund_rG_Platy",
                                 "log.1.rG_abund_rG_Lestodip", # marginal
                                 "log.vLG_abund_SG_Platy", # marginal
                                 "log.vLG_abund_vLG_Mymarid",
                                 "vLG.height.mean_vLG_Eulo", # marginal
                                 "vLG.height.mean_rG_Tory", "log.1.rG_abund_rG_Tory",
                                 "vLG_abund_vLG_Mesopol", "vLG.height.mean_vLG_Mesopol", 
                                 "vLG.height.mean_vLG_Platy", "log.vLG_abund_vLG_Platy",
                                 "vLG.height.mean_vLG_Tory", "log.vLG_abund_vLG_Tory")) %>% # vLG.height.mean is marginal for vLG_Tory
  select(predictor = X1, response = X2, coefficient = value)
arrange(sig.coef.df.2, predictor, response)
1 - exp(-0.2157298) # 19% decrease in vLG_Platy interaction with every one unit increase in gall size.
1 - exp(-0.2697011) # 24% decrease in vLG_Mesopolobous interaction with every one unit increase in gall size.
```

The results from the link composition analysis suggest that increases in gall abundance lead to increasing food web complexity for those individual nodes, whereas differences in leaf gall size lead to fundamental differences in link composition.

```{r}
row.count <- dim(full.predictors)[1]
arrange(full.predictors, vLG.height.mean)$vLG.height.mean

## generate a data frame that varies on Iteomyia abundance but holds all other variables constant at their means.
predict.log.vLG_abund <- with(full.predictors,
                              data.frame(log.vLG_abund = seq(from = min(log.vLG_abund),
                                                             to = max(log.vLG_abund),
                                                             length.out = row.count),
                                         vLG.height.mean = rep(mean(vLG.height.mean), row.count),
                                         log.1.rG_abund = rep(mean(log.1.rG_abund), row.count),
                                         log.1.aSG_abund = rep(mean(log.1.aSG_abund), row.count)))

## predict link abundance based on the Iteomyia abundance variation.
log.vLG_abund.predict <- predict(net.mvabund.2, 
                       newdata = predict.log.vLG_abund, 
                       type = "response", se.fit = TRUE) 
colnames(log.vLG_abund.predict$se.fit) <- colnames(log.vLG_abund.predict$fit) # set column names for SE
log.vLG_abund.fit.df <- cbind.data.frame(log.vLG_abund.predict$fit, 
                                             predict.log.vLG_abund)
log.vLG_abund.SE.df <- cbind.data.frame(log.vLG_abund.predict$se.fit,
                                        predict.log.vLG_abund)
log.vLG_abund.predict.df <- rbind.data.frame(log.vLG_abund.fit.df,
                                             log.vLG_abund.SE.df) %>%
  mutate(type = c(rep("predict", row.count),
                  rep("SE", row.count))) %>%
  select(-log.1.aSG_abund, -log.1.rG_abund, -vLG.height.mean) %>%
  melt(id.vars = c("type","log.vLG_abund")) %>%
  spread(type, value)

ggplot(data = filter(log.vLG_abund.predict.df, 
                     variable %in% c("vLG_Platy","vLG_Mesopol","vLG_Tory")),
       aes(x = exp(log.vLG_abund), y = predict)) + 
  geom_line(aes(color = variable)) +
  geom_ribbon(aes(ymax = predict + SE, ymin = predict - SE, fill = variable), alpha = 0.25) +
  ylab("Link density (#/branch)") + xlab("Leaf gall midge density (#/branch)")

## generate a data frame that varies on Iteomyia diameter but holds all other variables constant at their means.
predict.vLG.height.mean <- with(full.predictors,
                              data.frame(vLG.height.mean = seq(from = min(vLG.height.mean),
                                                             to = max(vLG.height.mean),
                                                             length.out = row.count),
                                         log.vLG_abund = rep(mean(log.vLG_abund), row.count),
                                         log.1.rG_abund = rep(mean(log.1.rG_abund), row.count),
                                         log.1.aSG_abund = rep(mean(log.1.aSG_abund), row.count)))

## predict link abundance based on the Iteomyia diameter variation.
vLG.height.mean.predict <- predict(net.mvabund.2, 
                       newdata = predict.vLG.height.mean, 
                       type = "response", se.fit = TRUE) 
colnames(vLG.height.mean.predict$se.fit) <- colnames(vLG.height.mean.predict$fit) # set column names for SE
vLG.height.mean.fit.df <- cbind.data.frame(vLG.height.mean.predict$fit, 
                                             predict.vLG.height.mean)
vLG.height.mean.SE.df <- cbind.data.frame(vLG.height.mean.predict$se.fit,
                                        predict.vLG.height.mean)
vLG.height.mean.predict.df <- rbind.data.frame(vLG.height.mean.fit.df,
                                             vLG.height.mean.SE.df) %>%
  mutate(type = c(rep("predict", row.count),
                  rep("SE", row.count))) %>%
  select(-log.1.aSG_abund, -log.1.rG_abund, -log.vLG_abund) %>%
  melt(id.vars = c("type","vLG.height.mean")) %>%
  spread(type, value)

ggplot(data = filter(vLG.height.mean.predict.df, 
                     variable %in% c("vLG_Platy","vLG_Mesopol","vLG_Tory","rG_Tory")),
       aes(x = vLG.height.mean, y = predict)) + 
  geom_line(aes(color = variable)) +
  geom_ribbon(aes(ymax = predict + SE, ymin = predict - SE, fill = variable), alpha = 0.25) +
  ylab("Link density (#/branch)") + xlab("Leaf gall diameter (mm)")

## generate a data frame that varies on bud gall density but holds all other variables constant at their means.
predict.log.1.rG_abund <- with(full.predictors,
                              data.frame(log.1.rG_abund = seq(from = min(log.1.rG_abund),
                                                             to = max(log.1.rG_abund),
                                                             length.out = row.count),
                                         log.vLG_abund = rep(mean(log.vLG_abund), row.count),
                                         vLG.height.mean = rep(mean(vLG.height.mean), row.count),
                                         log.1.aSG_abund = rep(mean(log.1.aSG_abund), row.count)))

## predict link abundance based on the bud gall variation.
log.1.rG_abund.predict <- predict(net.mvabund.2, 
                       newdata = predict.log.1.rG_abund, 
                       type = "response", se.fit = TRUE) 
colnames(log.1.rG_abund.predict$se.fit) <- colnames(log.1.rG_abund.predict$fit) # set column names for SE
log.1.rG_abund.fit.df <- cbind.data.frame(log.1.rG_abund.predict$fit, 
                                             predict.log.1.rG_abund)
log.1.rG_abund.SE.df <- cbind.data.frame(log.1.rG_abund.predict$se.fit,
                                        predict.log.1.rG_abund)
log.1.rG_abund.predict.df <- rbind.data.frame(log.1.rG_abund.fit.df,
                                             log.1.rG_abund.SE.df) %>%
  mutate(type = c(rep("predict", row.count),
                  rep("SE", row.count))) %>%
  select(-log.1.aSG_abund, -vLG.height.mean, -log.vLG_abund) %>%
  melt(id.vars = c("type","log.1.rG_abund")) %>%
  spread(type, value)

ggplot(data = filter(log.1.rG_abund.predict.df, 
                     variable %in% c("rG_Tory","rG_Eulo")),
       aes(x = exp(log.1.rG_abund), y = predict)) + 
  geom_line(aes(color = variable)) +
  geom_ribbon(aes(ymax = predict + SE, ymin = predict - SE, fill = variable), alpha = 0.25) +
  ylab("Link density (#/branch)") + xlab("Bud gall density (#/branch)")

## NOTE THAT IT IS N'T WORKING TO HAVE THE RAW DATA BECAUSE THE SEQUENCE DATA OF THE PREDICTOR VARIABLE MAY HAVE SOME OVERLAPPING VALUES IN ITS ORIGINAL FORM.

## generate a data frame that varies on Iteomyia diameter but holds all other variables constant at their means.
#log.1.aSG_abund.seq <- arrange(full.predictors, log.1.aSG_abund)$log.1.aSG_abund
#log.1.aSG_abund.OG <- arrange(full.predictors, log.1.aSG_abund)[ ,interaxns_noPont]
predict.log.1.aSG_abund <- with(full.predictors,
                              data.frame(log.1.aSG_abund = seq(from = min(log.1.aSG_abund),
                                                               to = max(log.1.aSG_abund),
                                                               length.out = row.count),
                                         log.vLG_abund = rep(mean(log.vLG_abund), row.count),
                                         vLG.height.mean = rep(mean(vLG.height.mean), row.count),
                                         log.1.rG_abund = rep(mean(log.1.rG_abund), row.count)))

## predict link abundance based on the Iteomyia diameter variation.
log.1.aSG_abund.predict <- predict(net.mvabund.2, 
                       newdata = predict.log.1.aSG_abund, 
                       type = "response", se.fit = TRUE) 
colnames(log.1.aSG_abund.predict$se.fit) <- colnames(log.1.aSG_abund.predict$fit) # set column names for SE
#log.1.aSG_abund.OG.df <- cbind.data.frame(log.1.aSG_abund.OG,
          #                                predict.log.1.aSG_abund)
log.1.aSG_abund.fit.df <- cbind.data.frame(log.1.aSG_abund.predict$fit, 
                                             predict.log.1.aSG_abund)
log.1.aSG_abund.SE.df <- cbind.data.frame(log.1.aSG_abund.predict$se.fit,
                                        predict.log.1.aSG_abund)
log.1.aSG_abund.predict.df <- rbind.data.frame(#log.1.aSG_abund.OG.df,
                                               log.1.aSG_abund.fit.df,
                                             log.1.aSG_abund.SE.df) %>%
  mutate(type = c(#rep("OG", row.count),
                  rep("predict", row.count),
                  rep("SE", row.count))) %>%
  select(-log.1.rG_abund, -vLG.height.mean, -log.vLG_abund) %>%
  melt(id.vars = c("type","log.1.aSG_abund")) %>%
  spread(type, value) # was getting an error about duplicate row identifiers, but it seems to be okay..

ggplot(data = filter(log.1.aSG_abund.predict.df, 
                     variable %in% c("aSG_Tory")),
       aes(x = exp(log.1.aSG_abund), y = predict)) + 
  geom_line(aes(color = variable)) +
  geom_ribbon(aes(ymax = predict + SE, ymin = predict - SE, fill = variable), alpha = 0.25) +
  ylab("Link density (#/branch)") + xlab("apical-Stem gall density (#/branch)")

# incorrectly plot the data with all of the points...not controlling for any other predictors though which are important...
test <- dplyr::select(full.predictors, vLG.height.mean, log.vLG_abund, log.1.rG_abund, vLG_Tory, vLG_Platy, vLG_Mesopol, rG_Tory, rG_Eulo)
test2 <- melt(as.data.frame(test), id.vars = c("vLG.height.mean", "log.vLG_abund", "log.1.rG_abund"))
test2 <- mutate(test2, value.bin = ifelse(value > 0, 1, 0))
test2 <- mutate(test2, log.vLG.cut = ifelse(log.vLG_abund < 1.343, 0, 1))

summary(full.predictors$log.vLG_abund)

library(MASS)
ggplot(filter(test2, variable %in% c("vLG_Tory","vLG_Platy","vLG_Mesopol")), aes(x = vLG.height.mean, y = value, color = factor(log.vLG.cut))) + geom_point() + geom_smooth(method = "glm.nb") + facet_wrap( ~ variable, ncol = 3)
ggplot(filter(test2, variable %in% c("vLG_Tory","vLG_Platy","vLG_Mesopol","rG_Tory")), aes(x = vLG.height.mean, y = value.bin)) + geom_point() + geom_smooth(method = "glm", family = "binomial") + facet_wrap( ~ variable, ncol = 1)

test3 <- glmer(vLG_Platy ~ vLG.height.mean + log(vLG_abund) + (1|Genotype), full.predictors, family = poisson)
overdisp_fun(test3) # no overdispersion
summary(test3)
plot(test3) # residuals don't look great though
visreg(test3, scale = "response", partial = TRUE) # why is the vLG_Platy point so high with the vLG_abund? It is impossible...but may suggest poor model fit, since these are the partial residual plots (ref: https://github.com/pbreheny/visreg/issues/1). Note however, that this issue is much improved when I used a genearlized linear mixed effects models
```
